CFHTLens Weak Lensing Emulator and Cosmological Constraints from the Minkowski Functionals and Moments

### 2014-12-02 Paper_minkowski/paper.tex
update generate.py and paper.tex
update figures and paper

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{Figures/contours_3comp.png}
\end{center}
\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the $V_0$ (red), $V_1$ (blue), $V_2$ (green), LM (black) and Power Spectrum (orange) statistics; the two panels are obtained marginalizing the parameter likelihood (\ref{parameterlikelihood}) over $w$ (left panel) and conditioning it on the plane $w=-1.0$ (right panel)}
\label{contours3comp}
\end{figure*}

@@

\subsection{Robustness}

>>>>

\subsection{Robustness}
%
The purpose of this paragraph is to convince the reader that the cosmological constraints we show in this paper are numerically robust, i.e. they are reasonably stable once we consider an increasing number of Principal Components. These stability plots are shown in Figure

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.4]{Figures/contours_3comp.pdf}
\end{center}
\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the $V_0$ (red), $V_1$ (blue), $V_2$ (green), LM (black) and Power Spectrum (orange) statistics; the two panels are obtained marginalizing the parameter likelihood (\ref{parameterlikelihood}) over $w$ (left panel) and conditioning it on the plane where $w$ corresponds to its best fit value (right panel)}
\label{contours3comp}
\end{figure*}

@@
